The Stakes of Scrying: \lstinline[style=inlinecode]{.^} dotket and the Seer Proposal

### 2024-02-06 mss.tex
Post near-final draft.

\newcommand{\authorname}{Ted Blackman~\patp{rovnys-ricfer} and Paul Driver~\patp{fodwyt-ragful}}
\newcommand{\authorpatp}{}
\newcommand{\affiliation}{Urbit Foundation}

@@

\begin{lstlisting}[style=listingcode]
++  on-poke
  |=  [m=mark v=vase]
  ^-  (quip card _this)
  =/  foo-result  .^  @da  /cx/(now)/foo
  ::  do something with foo-result...
  [~ this]
\end{lstlisting}

@@

\bibliographystyle{plainnat}
\bibliography{ustj-dotket}
\end{document}

>>>>

\addbibresource{mss.bib}

\newcommand{\authorname}{Ted Blackman~\patp{rovnys-ricfer} \\ Paul Driver~\patp{fodwyt-ragful}}
\newcommand{\authorpatp}{}
\newcommand{\affiliation}{Urbit Foundation}

@@

\begin{lstlisting}[style=listingcode]
++  on-poke
  |=  [m=mark v=vase]
  ^-  (quip card _this)
  =/  foo-result  .^(@da /cx/(scot %da now)/foo)
  ::  do something with foo-result...
  [~ this]
\end{lstlisting}

@@

\printbibliography
\end{document}
